Building Large-Scale Cross-lingual Knowledge Base from Multi-Wiki

### 2015-06-06 nlpcc/paper.tex
丢失的改动。 删了两张图片

However, most non-English knowledge in those knowledge bases is pretty scarce. Figure \ref{fig_stat} shows a simplified long tail distribution of the number of articles on six major Wikipedia language versions. Due to the imbalance of different Wikipedia language versions, the knowledge distribution across different languages is highly unbalanced in those knowledge bases which are generated from Wikipedia. For instance, DBpedia contains 4.58 million English instances but only XXX Chinese instances. On the other hand, the Chinese Hudong Baike\footnote{{\tt http://www.baike.com/}} and Baidu Baike\footnote{{\tt http://baike.baidu.com/}}, both containing more than 6 million articles, are even larger than the English Wikipedia. If a knowledge base could be established between English Wikipedia and Chinese Hudong Baike, an English-Chinese knowledge base with much higher coverage in Chinese can be constructed.
\begin{figure}[h]
\centering
  \includegraphics[width=11cm]{fig/fig_stat.png}\\
  \caption{Number of Articles on Major Wikipedias, Baidu Baike and Hudong Baike}
  \label{fig_stat}
\end{figure}

To enrich the Chinese knowledge, we try to build a large-scale English-Chinese knowledge base by semantifying four heterogeneous online wikis, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike. In this paper, we propose a unified framework to build such a knowledge base. The framework contains three steps: extracting dataset from online wikis, extending an initial language link set, and pruning taxonomy for more precise semantic relation. The generated knowledge base contains 663,740 classes, 11,721,238 instances and 56,449 properties. An online system supporting keyword search and SPARQL endpoint is also developed.

This non-trivial task poses the challenges as follows:
\begin{enumerate}
  \item The cross-lingual links are highly limited inside Wikipedia. For instance, there are only 9\% English-Chinese matched articles in Wikipedia in all articles. How could we find enough English-Chinese \verb"owl:sameAs" relations?
  \item The subsumption relations of the online wikis' category systems contain lots of noise. For example, in English Wikipedia ``Wikipedia-books-on-people", which is actually \verb"subClassOf" ``Books", is taken as the sub-category of ``People" mistakenly. How could we detect those incorrect semantic relations?
\end{enumerate}

Driven by these challenges, we propose a unified framework to build a English-Chinese knowledge base from four heterogeneous online wikis. Specifically, our work makes the following contributions.
\begin{enumerate}
  \item We achieve refined datasets from multiple heterogeneous online wikis through unified extracting process. 
  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations in ontology.
  \item Both online-system and SPARQL endpoint are provided for public query operations over our knowledge base.
\end{enumerate}

@@

\subsection{Wiki Pages}
Articles from the four sources are similar in structure. Usually they provide two important elements with potential semantic information, category system and articles. A category system represents the relations between categories as a tree by the relation \textit{subCategoryOf}. Fig.\ref{fig:hudong-taxonomy} shows a screenshot of Hudong Taxonomy. An article describes an entity with rich information created and modified by several verified editors. Besides, each article is linked to one or more categories by \textit{articleOf} relation. In general, there are five elements can be exploited in each article page:
\begin{figure}
    \centering
    \begin{minipage}[t]{0.8\textwidth}
        \centerline{\includegraphics[width=0.8\columnwidth]{fig/hudong-taxonomy2}}
        \caption{Taxonomy in Hudong}
        \label{fig:hudong-taxonomy}
    \end{minipage}%
\end{figure}
\begin{itemize}
  \item Title: A Title is the label of an entity, which is unique so that it can be used to distinguish entities.
  \item Abstract: An abstract is a brief summary of the entity. It's always the first paragraph of an article.
  \item Infobox: Most of articles contain infobox. An infobox maintains structured data which are subject-attribute-value triples formalized as a table. Information in this table includes important properties of an entity.
  \item Links: Links are entries to other articles within the encyclopedia. They lead readers to reference articles. 
  \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article has \textit{articleOf} relation with its categories.
  \item URL: Each article has an HTTP url to identify itself on web.
\end{itemize}

Fig. \ref{fig:interstellar} shows a snap of an article in Chinese Wikipedia.
\begin{figure}[ht]
    \centerline{\includegraphics[width=1\columnwidth]{fig/interstellar}}
    \caption{A snap of Interstellar(Film) article in Chinese Wikipedia}
    \label{fig:interstellar}
\end{figure}%

The elements of each article $a$ can be defined as follow:
\begin{equation}
    a = <Ti(a),Ab(a),Li(a),In(a),C(a),U(a)>
\end{equation}
where $Ti(a),Ab(a),Li(a),In(a),C(a),U(a)$ denotes title, abstract, links, infobox, category tags, url of article $a$.

Notably, articles in Wikipedia follow templates specified by Wikipedia when being edited. A template defines items that a group of article should fill. Besides, infoboxes are also generated based on certain templates recommended by Wikipedia. For example, The infobox in film 星际穿越(Interstellar) is edited according to the Template \emph{Infobox film}, which maintains a property set of films. An Infobox $In(a)$ contains a set of attribute-value pairs {$p_{1}$, $p_{2}$,...}. We denote infobox template as $T(a)$. Templates specify certain attributes, which are usually different from those displayed on the webpage. Thus, we define an attribute-value pair as a triple $p=<tl,dl,v>$, where $tl$ is attribute label in template, $dl$ is displayed label in web page and $v$ is the corresponding value. The value maybe a text or a reference to another entity.

Moreover, in Wikipedia, some article pages have language links which help readers switch to other language-version within the same article. Fig. \ref{fig:interstellar}shows language links of \emph{Interstellar} on the right column of the Wikipedia page. As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article links, usually titles, in English and Chinese separately. Thus, to a $cl$ in $CL$, $cl(a) = <L_{e}(a), L_{z}(a)>$.

@@

In this paper, our task is to build an Cross-lingual Knowledge Base(CLKB) assembling knowledge from several English or Chinese encyclopedia sources. Given four encyclopedia datasets $W_{1},W_{2},W_{3},W_{4}$, we get $O_{i}$ including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, taxonomy $H^C_{i}$ of each dataset $W_{i}$ by extracting. We then enrich the extracted language-link set $CL$ using an link-discovery extension method. We also refining taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship. Our final output is an English-Chinese ontology  with SPARQL endpoint though process of combine $O_{i}$ by utilizing language links in $CL$.

The whole building procedure is shown in Fig. \ref{fig:procedure}
\begin{figure}[ht]
    \centerline{\includegraphics[width=1\columnwidth]{fig/procedure2}}
    \caption{Procedure of building our cross-lingual knowledge base}
    \label{fig:procedure}
\end{figure}%
We extract information from four sources, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia. Considering the different data format of each source, that is, html code page of Baidu and Hudong with different layout, and XML format of Wikipedia dump file, various extractors should be employed. After data parsing, we get four ontologies each source. Going through the process of taxonomy pruning, we delete some incorrect relations. At last Using the extended language links, we combine the four ontologies into a cross-lingual knowledge base.

\section{Semantic Data Extraction}
\label{sec:dp}
Semantic data extraction aims to achieve a structured dataset from the input encyclopedias, preparing for the knowledge base construction. Specifically, we extracts classes from category taxonomy, instances according to articles, and properties based on infoboxes and its templates.

@@

\subsubsection{Infobox-properties}
Attributes acquired from infobox are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox. The type of a property, datatype or object, depends on the type of the value. Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as objecttype. For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string. Meanwhile, 导演(directed by) can be an object property because its value points to a person who directed the movie.

We are challenged when extracting properties from infoboxes:
\begin{itemize}
    \item In Wikipedia, the attribute label displayed in the webpage infobox is inconsistent with it in the published dump file. Fig.\ref{fig:infobox-template} gives a mapping result of display labels and dump labels in \emph{Interstellar}' infobox. The left is infobox, the middle is a snap from dump file in Wikipedia. As we've seen, attribute label in infobox is different from it in dump file. We explore the display labels as property labels in Wikipedia rather than dump labels extracted from raw data.
    \begin{figure}[ht]
        \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template}}
        \caption{Comparison of display label and dump label in \emph{Interstellar} infobox}
        \label{fig:infobox-template}
    \end{figure}%
\item There are special characters in labels. Wikipedia usually uses hyphen "-" or dot "•" to mark sublabels. For example, \emph{population} property has sub-properties "-Density" and "-Urban". In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
\end{itemize}

To solve the problems above, we take advantage of template information. Specifically, Wikipedia institutes rules of rendering label in templates. For example, movie infobox follows template \emph{Infobox film}, which is shown on the right of Fig.\ref{fig:infobox-template}, where both display labels and dump labels come from. When a dump label occurs in dump file, we replace it by its mapping display label.

@@

We harvest four types of information during this stage. (1) General-properties of instance, including title as label property value, first paragraph as abstract property value and HTTP URL as URL property value. (2) Infobox-properties which are acquired via extracting from the infobox in the article; (3) $articleOf$ relation with categories listed at the bottom of article page. For example, 美国科幻片(American science fiction films) is a category of Interstellar; (4) Reference relation with other instances according to links in the content. We gain the reference $Li(a)$ between the current instance and others, such as 华纳兄弟(Warner Bros.).

@@

To construct a cross-lingual knowledge base with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set. Secondly, we integrate this four encyclopedias, which is to say, respectively merging concepts, instances and properties from the four sources if they represent the same thing. Thirdly, we prune the taxonomy generated from concept relationships to make it more accurate. At last, we make instances and properties attached to complete the cross-lingual knowledge base construction.

\subsection{Cross-lingual Linking}
There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of concepts and instances. Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set. With the linkage factor graph model, we harvest a cross-lingual links extension as many as 20 thousands with an ideal precision 85.5\% and a recall of 88.1\% between English Wikipedia and Baidu Baike.

@@

However, due to using templates, Infobox-properties have no obvious cross-lingual links. To acquire such links, we take the following steps:
\begin{enumerate}[1)]
    \item Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same dump label. That is to say, to $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
    \item Given the English and Chinese infoboxes of two matched articles $a_{e}$ and $a_{z}$ direct to the same entity, compare their templates, English template $T_{e}(a_{e})$ and Chinese template $T_{z}(a_{z})$, find the matched display labels mapping to the same dump label; 
    \item Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; for object properties, check whether the value refer to the same entity.
\end{enumerate}

>>>>

However, most non-English knowledge in those knowledge bases is pretty scarce. Figure \ref{fig_stat} shows a simplified long tail distribution of the number of articles on six major Wikipedia language versions. Due to the imbalance of different Wikipedia language versions, the knowledge distribution across different languages is highly unbalanced in those knowledge bases which are generated from Wikipedia. For instance, DBpedia contains 4.58 million English instances but only XXX Chinese instances. On the other hand, the Chinese Hudong Baike\footnote{{\tt http://www.baike.com/}} and Baidu Baike\footnote{{\tt http://baike.baidu.com/}}, both containing more than 6 million articles, are even larger than the English Wikipedia. If a knowledge base could be established between English Wikipedia and Chinese Hudong Baike, an Chinese-English knowledge base with much higher coverage in Chinese can be constructed.
\begin{figure}[h]
\centering
  \includegraphics[width=11cm]{fig/fig_stat.png}\\
  \caption{Number of Articles on Major Wikipedias, Baidu Baike and Hudong Baike}
  \label{fig_stat}
\end{figure}

To enrich the Chinese knowledge, we try to build a large-scale Chinese-English knowledge base by semantifying four heterogeneous online wikis, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike. In this paper, we propose a unified framework to build such a knowledge base. The framework contains three steps: extracting dataset from online wikis, extending an initial language link set, and pruning taxonomy for more precise semantic relation. The generated knowledge base contains 663,740 classes, 11,721,238 instances and 56,449 properties. An online system supporting keyword search and SPARQL endpoint is also developed.

This non-trivial task poses the challenges as follows:
\begin{enumerate}
  \item The cross-lingual links are highly limited inside Wikipedia. For instance, there are only 9\% Chinese-English matched articles in Wikipedia in all articles. How could we find enough Chinese-English \verb"owl:sameAs" relations?
  \item The subsumption relations of the online wikis' category systems contain lots of noise. For example, in English Wikipedia ``Wikipedia-books-on-people", which is actually \verb"subClassOf" ``Books", is taken as the sub-category of ``People" mistakenly. How could we detect those incorrect semantic relations?
\end{enumerate}

Driven by these challenges, we propose a unified framework to build a Chinese-English knowledge base from four heterogeneous online wikis. Specifically, our work makes the following contributions.
\begin{enumerate}
  \item We achieve refined datasets from multiple heterogeneous online wikis through unified extracting process. 
  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations in ontology.
  \item Both online-system and SPARQL endpoint are provided for public query operations over our knowledge base.
\end{enumerate}

@@

\subsection{Wiki Pages}
Articles from the wiki sources are similar in structure. Usually they provide two important elements with potential semantic information, category system and articles. A category system represents the relations between categories as a tree by the relation \textit{subCategoryOf}. An article describes an entity with rich information created and modified by several verified editors. Besides, each article is linked to one or more categories by \textit{articleOf} relation. In general, there are six elements can be exploited in each article page:
%\begin{figure}
%    \centering
%    \begin{minipage}[t]{0.8\textwidth}
%        \centerline{\includegraphics[width=0.8\columnwidth]{fig/hudong-taxonomy2}}
%        \caption{Taxonomy in Hudong}
%        \label{fig:hudong-taxonomy}
%    \end{minipage}%
%\end{figure}
\begin{itemize}
  \item Title: A Title is the label of an entity, which is unique so that it can be used to distinguish entities.
  \item Abstract: An abstract is a brief summary of the entity. It's always the first paragraph of an article.
  \item Infobox: Most of articles contain infobox. An infobox maintains structured data which are subject-attribute-value triples formalized as a table. Information in this table includes important properties of an entity.
  \item Links: Links are entries to other articles within the encyclopedia. They represent the relations between the current article and others.
  \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article has \textit{articleOf} relation with its categories.
  \item URL: Each article has an HTTP url to identify itself on web.
\end{itemize}

%Fig. \ref{fig:interstellar} shows a snap of an article in Chinese Wikipedia.
%\begin{figure}[ht]
%    \centerline{\includegraphics[width=1\columnwidth]{fig/interstellar}}
%    \caption{A snap of Interstellar(Film) article in Chinese Wikipedia}
%    \label{fig:interstellar}
%\end{figure}%
%
The elements of each article $a$ can be defined as follow:
\begin{equation}
    a = <Ti(a),Ab(a),Li(a),In(a),C(a),U(a)>
\end{equation}
where $Ti(a),Ab(a),Li(a),In(a),C(a),U(a)$ denotes title, abstract, links, infobox, category tags, url of article $a$.

Notably, articles in Wikipedia follow templates specified by Wikipedia when being edited. A template defines items that a group of article should fill. Besides, infoboxes are also generated based on certain templates recommended by Wikipedia. For example, The infobox in film 星际穿越(Interstellar) is edited according to the Template \emph{Infobox film}, which maintains a property set of films. An Infobox $In(a)$ contains a set of attribute-value pairs {$p_{1}$, $p_{2}$,...}. We denote infobox template used in article $a$ as $T(a)$. Templates specify certain attributes, which are usually different from those displayed on the webpage. Thus, we define an attribute-value pair as a triple $p=<tl,dl,v>$, where $tl$ is attribute label in template, $dl$ is displayed label in web page and $v$ is the corresponding value. The value maybe a text or a reference to another entity.

Moreover, in Wikipedia, some article pages have language links which help readers switch to other language-version within the same article. Fig. \ref{fig:interstellar}shows language links of \emph{Interstellar} on the left column of the Wikipedia page. As to an article $a$ containing multi-language content in Wikipedia, $L_{e}$ and $L_{z}$ denotes its article links, usually titles, in English and Chinese separately. Thus, to a $cl \in CL$, $cl(a) = <L_{e}(a), L_{z}(a)>$.

@@

In this paper, our task is to build a CLKB assembling knowledge from several English or Chinese encyclopedia sources. Given four encyclopedia datasets $W_{1},W_{2},W_{3},W_{4}$, we get $O_{i}$ including class list $C_{i}$, instance list $I_{i}$, property list $P_{i}$, taxonomy $H^C_{i}$ of each dataset $W_{i}$ by extracting. We then enrich the extracted language-link set $CL$ using an link-discovery extension method. We also refining taxonomy by checking if an \textit{articleOf} or \textit{subCategoryOf} is really an \textit{instanceOf} or \textit{subClassOf} relationship. Our final output is an Chinese-English ontology  with SPARQL endpoint though process of combining $O_{i}$ by utilizing language links in $CL$.

The whole building procedure is shown in Fig. \ref{fig:procedure}
\begin{figure}[ht]
    \centerline{\includegraphics[width=1\columnwidth]{fig/procedure2}}
    \caption{Procedure of building our cross-lingual knowledge base}
    \label{fig:procedure}
\end{figure}%
We extract information from four sources, Baidu Baike, Hudong Baike, Chinese Wikipedia and English Wikipedia. Considering the different data format of each source, that is, html code page of Baidu and Hudong with different layout, and XML format of Wikipedia dump file, various extractors should be employed. After data parsing, we get four ontologies each source. Going through the process of taxonomy pruning, we delete some incorrect relations. At last using the extended language links, we combine the four ontologies into our CLKB

\section{Semantic Data Extraction}
\label{sec:dp}
Semantic data extraction aims to achieve a structured dataset from the input encyclopedias. Specifically, we extract classes from category system, instances according to articles, and properties based on infoboxes and their templates.

@@

\subsubsection{Infobox-properties}
Attributes acquired from infobox are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox. The type of a property, datatype or object, depends on the type of the value. Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as objecttype. For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string. Meanwhile, 导演(directed by) is an object property because its value points to a person who directed the movie.

We are challenged when extracting properties from infoboxes:
\begin{itemize}
    \item In Wikipedia, the attribute label displayed in the webpage infobox is inconsistent with it in the published dump file. Fig.\ref{fig:infobox-template} gives a mapping result of display labels and dump labels in \emph{Interstellar}' infobox. The left is infobox, the middle is a snap from dump file in Wikipedia. We explore the display labels as property labels in Wikipedia rather than dump labels extracted from raw data.
    \begin{figure}[ht]
        \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template}}
        \caption{Comparison of display label and dump label in \emph{Interstellar} infobox}
        \label{fig:infobox-template}
    \end{figure}%
\item There are special characters in labels. Wikipedia usually uses hyphen "-" or dot "•" to mark sublabels. For example, attribute \emph{population} property has sub-properties "-Density" and "-Urban". In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
\end{itemize}

To solve the problems above, we take advantage of template information. Specifically, Wikipedia institutes rules of rendering label in templates. Right of Fig.\ref{fig:infobox-template} shows an example of template \emph{Infobox film}, where corresponding relations of display labels and dump labels come from. When a dump label occurs in dump file, we replace it by its mapping display label.

@@

We harvest four types of information during this stage. (1) General-properties of instance, including title as label property value, first paragraph as abstract property value and HTTP URL as URL property value. (2) Infobox-properties which are acquired via extracting from the infobox in the article; (3) $articleOf$ relation with categories listed at the bottom of article page. For example, \textit{美国电影作品(American films)} is a category of \textit{Frozen}; (4) Reference relation with other instances according to links in the content, such as 冰雪女王(The Snow Queen).

@@

To construct a CLKB with existing structured data, firstly we gather cross-lingual links which can help match the same entity in two languages and extend the link set. Secondly, we integrate this four encyclopedias, which is to say, respectively merging classes, instances and properties from the four sources if they represent the same thing. Thirdly, we prune the taxonomy generated from class relationships to make it more accurate.

\subsection{Cross-lingual Linking}
There are \textcolor{red}{number} cross-lingual links between English and Chinese, which constitute the initial cross-lingual link set of classes and instances. Moreover, we utilize the language-independent method in \cite{wang2012cross} to extend the language-link set. With the linkage factor graph model, we harvest a cross-lingual links extension as many as 20 thousands with an ideal precision 85.5\% and a recall of 88.1\% between English Wikipedia and Baidu Baike.

@@

However, due to using templates, Infobox-properties have no obvious cross-lingual links. Thus, we take the following steps to solve the problem:
    \item Given two matched templates, $T_{e}$ and $T_{z}$, find the display labels mapping the same dump label. That is to say, to $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
    \item Given the English and Chinese infoboxes of two matched articles $a_{e}$ and $a_{z}$ direct to the same entity, compare their templates, English template $T_{e}(a_{e})$ and Chinese template $T_{z}(a_{z})$, find the matched display labels mapping to the same dump label; 
    \item Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; for object properties, check whether the value refer to the same entity.
\end{enumerate}
